Review Paper Draft

### 2020-07-03 main.tex
A few notes from 2020-07-02 meeting

 \anna{in organic chemistry cis means 'on the same side' and trans 'on the other side' so I thought cis/trans might be more descriptive for gamma structure than homo/heterogeneous. These are also used to describe gender identity, which is obviously not how I'm using it, so I don't want it to be confusing.}
 To evaluate the performance of penalized LMM methods in both scenarios, we consider exponential and dichotomous effect magnitudes with are (1) \anna{homogeneous/cis}, or (2) \anna{heterogeneous/trans} in nature for a total of four distinct $\bgamma$ structures. We define \anna{homogenous/cis} effects as those that are similar among genetically similar subpopulations, and \anna{heterogeneous/trans} effects as those that are not. Figure \ref{fig:gamma_structures} displays a visual summary of these coefficient structures. \anna{is this still unclear? Would a PCA picture help?}
\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/gamma_structure.png}
    \caption{$\bgamma$ structures}
    \label{fig:gamma_structures}
\end{figure}

>>>>

 \anna{CONCORDANT/DISCORDANT... synchronous/asynchronous}
 To evaluate the performance of penalized LMM methods in both scenarios, we consider exponential and dichotomous effect magnitudes with are (1) \anna{homogeneous/cis}, or (2) \anna{heterogeneous/trans} in nature for a total of four distinct $\bgamma$ structures. We define \anna{homogenous/cis} effects as those that are similar among genetically similar subpopulations, and \anna{heterogeneous/trans} effects as those that are not. Figure \ref{fig:gamma_structures} displays a visual summary of these coefficient structures. \anna{is this still unclear? Would a PCA picture help?}
\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.9]{figures/gamma_structure.png}
    \caption{$\bgamma$ structures}
    \label{fig:gamma_structures}
\end{figure}
